### 2020-05-28 paper.tex
Start Validation

We will conclude this introductory section with the clarification of important terms. Section~\ref{sec:interviews} presents the interview results along with the collected war stories and formalizes two recurrent challenges. With Section~\ref{sec:discussion}, we will have a look at current and previous research regarding debugging of reactive applications as well as specific tooling. We are going to validate presented challenges against currently available tools within Section~\ref{sec:study}, show threats to validity of our work in Section~\ref{sec:threats} and finally end with an outlook on future iterations.

@@

Reactive programming \emph{(RP)} is a declarative programming paradigm. Where engineers use imperative programing languages to tell a program every step \emph{how} to do something, a declarative language allows to describe \emph{what} wants to be achieved. The languages runtime system then figures out a way to satisfy that given description. RP environments specifically provide abstractions to describe a data-flow and dependency graph which is used to transform and direct data at runtime.

@@

\section{Study Design}
\label{sec:study}

\begin{itemize}
	\item Hypothesis
	\item Use prev section to build experiments using existing tooling
	\item Validate stories and interviews
\end{itemize}

>>>>

We will conclude this introductory section with the clarification of important terms. Section~\ref{sec:interviews} presents the interview results along with the collected war stories and formalizes two recurrent challenges. With Section~\ref{sec:discussion}, we will have a look at current and previous research regarding debugging of RAs as well as specific tooling. We are going to validate presented challenges against currently available tools within Section~\ref{sec:study}, show threats to validity of our work in Section~\ref{sec:threats} and finally end with an outlook on future iterations.

@@

RP is a declarative programming paradigm. Where engineers use imperative programing languages to tell a program every step \emph{how} to do something, a declarative language allows to describe \emph{what} wants to be achieved. The languages runtime system then figures out a way to satisfy that given description. RP environments specifically provide abstractions to describe a data-flow and dependency graph which is used to transform and direct data at runtime.

@@

\section{Validation of Interviews and War Stories}
\label{sec:study}

\subsection{Study Design}

\begin{itemize}
	\item \emph{Hypothesis: If frontend engineers are given an RxJS-based problem, then they will modify the code in order to understand its behavior.}
\end{itemize}
